Every Author as First Author

### 2023-03-27 paper.tex
Flesh out Section 2

@@

\usepackage{transparent}
\newcommand\namestack[1]{\texttransparent{0.666}{\textstack{#1}}}

@@

In our own writing, we try to avoid this practice, and instead
write all authors' last names whenever citing a paper,
e.g., ``X, Y, and Z~[\#]''.
But this workaround becomes impractical for references with ten or more authors.

@@

@@

To improve legibility, we write each name in semi-transparent ink
(currently, $2/3$ opacity).
As a result, where multiple characters overlap, the ink appears darker,
making the names more legible.%
%
\footnote{Warning: Not all PDF viewers correctly display text transparency
  as created by \texttt{transparent.sty}.  Notably, Adobe Acrobat on Windows
  does not seem to darken where multiple layers overlap.}
%
Compare:
%
\begin{itemize}
\item Opacity $1$\phantom{${}/1$}:
  \texttransparent{1}{\textstack{Erik Demaine; Martin Demaine}}
\item Opacity $3/4$:
  \texttransparent{0.75}{\textstack{Erik Demaine; Martin Demaine}}
\item Opacity $2/3$:
  \texttransparent{0.666}{\textstack{Erik Demaine; Martin Demaine}}
\item Opacity $1/2$:
  \texttransparent{0.5}{\textstack{Erik Demaine; Martin Demaine}}
\end{itemize}
%
In the future, we may consider using a different opacity depending on the
number of authors.  More extreme, we could use opacity to indicate the
relative contribution of each author (when they are unequal), or different
colors to represent different roles (such as supervisor).
But for now we like the uniformity of every name
appearing the same in all contexts.

@@

>>>>

\usepackage[utf8]{inputenc}

@@

\usepackage{transparent}
\newcommand\namestack[2][0.666]{\texttransparent{#1}{\textstack{#2}}}

@@

In our own writing, we try to avoid this practice, and instead
write all authors' last names whenever citing a paper,
e.g., ``X, Y, and Z~[\#]''.
But this workaround becomes impractical for references with over a dozen
authors, such as some of our papers
\cite{ArithmeticGames_ISAAC2020,LessThanEdgeMatching_JIP}
% >>> lines=open('edemaine.bib').read().split('\n')
% >>> import re
% >>> lines=[(len(re.findall(r'\band\b', line))+1, line) for line in lines]
% >>> sorted(lines)[-10:]
or some papers in astronomy \cite{reverse-alphabetical} and
biology \cite{human-genome}.

@@

Our vision is that each set of names (as we often associate with each paper)
becomes recognizable as its own image.  Readers can then recognize repetitions
of the same paper without necessarily reading the individual names.
For example, compare two of our papers with overlapping but differing sets
of 15 authors each:
\citet{ArithmeticGames_ISAAC2020} vs.\ \citet{LessThanEdgeMatching_JIP}.
Each author stack has a distinct shape.
If we now repeat one --- \citet{ArithmeticGames_ISAAC2020} ---
you should be able to recognize which it is.

\subsection{Revealing the Names}

Of course, we want to give authors (equal) credit for their papers,
not remove all credit.
We have implemented two ways to reveal the actual names present in a stack.

First, hovering over the stacked names should pop up a tooltip with the
authors listed in their original order.
In practice, PDF viewers do not seem to display the tooltips for text that is
also a link to the bibliography, so readers must click on the link and then
hover over the name stack in the bibliography; hopefully this extra step
will be unnecessary in the future.

Second, copying and pasting the author stack (together with any surrounding
text) into another document should reveal the authors in their original order,
using PDF's accessibility feature.  This makes it easy to quote portions of
a paper, including any citations, with or without author stacks.

@@

To improve legibility, we write each name in semi-transparent ink
(currently, $2/3$ opacity).
As a result, where multiple characters overlap, the ink appears darker,
making the names more legible.%
%
\footnote{Warning: Not all PDF viewers correctly display text transparency
  as created by \texttt{transparent.sty}.  Notably, Adobe Acrobat on Windows
  does not seem to darken where multiple layers overlap.}
%
Compare:
%
\begin{itemize}
\item \namestack[1]{Erik Demaine; Martin Demaine} ~ (opacity $1$, no transparency)
\item \namestack[0.75]{Erik Demaine; Martin Demaine} ~ (opacity $3/4$)
\item \namestack[0.666]{Erik Demaine; Martin Demaine} ~ (opacity $2/3$)
\item \namestack[0.5]{Erik Demaine; Martin Demaine} ~ (opacity $1/2$)
\end{itemize}
%
In the future, we may consider using a different opacity depending on the
number of authors.  More extreme, we could use opacity to indicate the
relative contribution of each author (when they are unequal), or different
colors to represent different roles (such as supervisor).
But for now we like the uniformity of every name
appearing the same in all contexts.

@@

\subsection{\LaTeX}

\subsection{\textsc{Bib}\TeX}

\subsection{HTML}
